%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans,unicode]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{selinput}
\SelectInputMappings{%
  adieresis={ä},
  eacute={é},
  Lcaron={Ľ},
}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Roberto} % Your first name
\familyname{Brunetti} % Your last name
\title{CV}

\homepage{www.sites.google.com/view/roberto-brunetti}{Personal webpage}  
\email{roberto.brunetti@assas-universite.fr}
 % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
 
 
\address{Born in Frascati (IT), 30/11/1994}{Last update: May 2026}

 

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	CURRENT POSITIONS
%----------------------------------------------------------------------------------------

\section{Current position}


\cventry{2025-Present}{Assistant professor (\textit{maître de conférences})}{\textsc{LEMMA - University of Paris Panthéon-Assas}}{France}{}{}

\cventry{2025-Present}{Associate researcher}{\textsc{GATE}}{France}{}{}



%----------------------------------------------------------------------------------------
%	ACCADEMIC POSITIONS
%----------------------------------------------------------------------------------------

\section{Previous positions}
\cventry{}{s}{}{}{}

\cventry{2023-2025}{Postdoctoral researcher}{\textsc{GATE - University of Lyon 2}}{France}{}{}

\cventry{2021-2023}{Lecturer (ATER)}{\textsc{University of Rennes}}{France}{}{}

\cventry{2018-2022}{Ph.D in Economics (Defense 12/12/2022)}{\textsc{CREM - University of Rennes}}{France}{}{Dissertation: Spatial Sources of Inequalities and Determinants of Redistribution\\ Committee: Marius Br\"{u}lhart, Etienne Lehmann (referee), Beno\^{i}t Le Maux, \\ Fabien Moizeau (supervisor), Alain Trannoy (referee), Elisabet Viladecans-Marsal} 

\cventry{Fall 2021}{Visiting fellow}{\textsc{HEC - University of Lausanne}}{Switzerland}{Host: Pr.Marius Br\"{u}lhart}{} 


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Education}


\cventry{2016-2018}{MSc in Economics}{\textsc{University of Turin}}{Italy}{110 summa cum laude \& honorable mention}{} 


\cventry{2017-2018}{MSc in Economics}{\textsc{University of Rennes}}{France}{Double Degree}{}

\cventry{2013-2016}{BA in Economics }{\textsc{University of Rome Tor Vergata}}{Italy}{110 summa cum laude}{}

\cventry{2015-2016}{Exchange program (Erasmus)}{\textsc{University of Hertfordshire}}{United Kingdom}{}{}


%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\section{Research interests}

\cvitem{}{Public Economics, Political Economy, Experimental Economics, Applied Microeconomics, Urban Economics}


%----------------------------------------------------------------------------------------
%	WORK IN PROGRESS
%----------------------------------------------------------------------------------------

\section{Publications}

\begin{itemize}
	\item Delemazure, T., Baujard, A., Brunetti, R., and Bouveret, S. (2026) \textbf{Do Grades Have Absolute Meaning? An Experiment on Majority Judgment.} \underline{Social Choice \& Welfare}, Forthcoming \href{https://hal.science/hal-05114129}{[\textcolor{blue}{Link to paper}]}
	\item Brunetti, R., Gaigné, C., and Moizeau, F. (2026) \textbf{Land, Wealth, and Taxation}. \underline{AEJ: Microeconomics}, Forthcoming \href{https://drive.google.com/file/d/1YlqsoiDjfmEGi_3gS3_R8PQSKRM_npho/view?usp=sharing}{[\textcolor{blue}{Link to paper}]}
	\item Brunetti, R. and Pourieux, M. (2026). \textbf{Representative policymakers? A behavioural experiment with French politicians.} \underline{Economica}, 1-32. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/ecca.70043}{[\textcolor{blue}{Link to paper}]}
    \item Baujard, A., Brunetti, R., Lebon, I., \& Marsilio, S. (2025). \textbf{How people understand voting rules.} \underline{Public Choice }\href{https://link.springer.com/article/10.1007/s11127-025-01344-8}{[\textcolor{blue}{Link to paper}]}
    \item Brunetti, R., Gaigné, C. \& Moizeau, F. (2023). \textbf{Credit Market Imperfections, Urban Land Rents, and the Henry George Theorem.} \underline{Revue économique}, 74, 681-703. \href{https://www.cairn.info/revue-economique-2023-5-page-681.htm}{[\textcolor{blue}{Link to paper}]}
\end{itemize}

\section{Working papers}

\begin{itemize}

    \item \textbf{Trickle-Down Economics, Merit, and Redistribution: An Experiment with the Poorest and Richest US Americans} (with Gianluca Grimalda and Maria Marino) \href{https://hal.science/hal-05112815}{[\textcolor{blue}{Working paper}]} 
    \item \textbf{Municipalities' Voting Power and Housing Supply: Evidence from French Intermunicipal Cooperation} \href{https://drive.google.com/file/d/1-29URpTjNFOBph_mNWi0YyPggXbfts_v/view}{[\textcolor{blue}{Working paper}]}
\end{itemize}

\section{Selected work in progress}

\begin{itemize}

    \item \textbf{Open deliberation and bargaining} (with João V. Ferreira and Benoit Tarroux) [Design]
    \item \textbf{The Determinants of Municipalities' Mergers} (with Pauline Mille and Sonia Paty) 
    \item \textbf{Merit, Environmental Externalities, and Redistribution: An Experiment} (with Federico Gonzalez, Maria Marino, and Johanna Mollerstrom)
    \item \textbf{Approval voting with different number of candidates: An experiment} (with Antoinette Baujard, Théo Delemazure, and Jerome Lang)
\end{itemize}

%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------

\section{Presentations at conferences, seminars and workshops}

\cvitem{2025}{Seminar at LED (University of Paris VIII); JPO Paris Dauphine; JPO Paris Nanterre; Seminar - University of Paris II (LEMMA)}

\hspace{2mm}

\cvitem{2024}{Conference of the French Association of Experimental Economics (University of Grenoble); The Society for Social Choice and Welfare meeting (Paris School of Economics); The Public Economic Theory Conference (University of Lyon 2); In\_equality conference (University of Konstanz); The poster session of the Amsterdam/Saint-Etienne Workshop on Social Choice; Séminaire - University of Barcelona, Faculty of Economics and Business}

\hspace{2mm}

\cvitem{2023}{ADRES (Université Paris-Dauphine); CREM Seminar (Université de Rennes); CISEPS Workshop (Università di Milano-Bicocca)}

\hspace{2mm}

\cvitem{2022}{European Meeting of the Urban Economics Association (LSE); Workshop EDGE (Université de Nantes); Journées de Microéconomie Appliquée (Université de Rennes), XXXIV annual conference of the Italian Society of Public Economics (Università de L'Aquila)}

\hspace{2mm}

\cvitem{2021}{North American Meeting of the Urban Economics Association (online); Workshop Economics and Politics @ Paris (Sciences Po Paris); XXXIII annual conference of the Italian Society of Public Economics (online); 3rd Swiss Workshop on Local Public Finance and Regional Economics (Università di Lugano); 3rd European association Young Economists Workshop (Online); GSW Seminar (University of Zurich and HEC Lausanne)}

\hspace{2mm}

\cvitem{2020}{Workshop EDGE (Online); Seminar of the \textit{Pôles RRC} (Online); Project Doc Seminar (Online)}

\hspace{2mm}

\cvitem{2019}{Workshop EDGE (Université de Rennes); Project Doc Seminar (Université de Rennes); PEARL conference, as a discussant (Université de Rennes)}

%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------

\section{Teaching}

\cvitem{2025/2026}{Macroeconomics (Bachelor, Université Paris Panthéon-Assas); Public economics (Bachelor, Université Paris Panthéon-Assas \& BA in Mauritius); Applied econometrics (Master, Université Paris Panthéon-Assas)}

\hspace{2mm}

\cvitem{2023/2024}{Economic inequality and preferences for redistribution (Master 2, Université Lumière Lyon 2)}

\hspace{2mm}

\cvitem{2022/2023}{Macroeconomics (Undergraduate, in French. TA of Pr. C. Gueguen); Microeconomics - Market imperfections (Undergraduate, in French. TA of Pr. E. Malin); Monetary Economics (Bachelor, in English. and in French. TA of Pr. T. Razafindrabe and C. Poutineau)}

\hspace{2mm}

\cvitem{2021/2022}{Microeconomics (Undergraduate, in French. TA of Pr. E. Avenel); Microeconomics - Market imperfections (Undergraduate, both in French and in English. TA of Pr. E. Malin and Pr. F. Padovano) Monetary Economics (Bachelor, in English. TA of Pr. T. Razafindrabe)}

\hspace{2mm}

\cvitem{2020/2021}{Microeconomics (Undergraduate, in French. TA of Pr. O. L'Haridon); Advanced Tax Theory (Master, in English. TA of Pr. F. Moizeau); Monetary Economics (Bachelor, in English. TA of Pr. T. Razafindrabe); Macroeconomics (Bachelor, in English. TA of Pr.M.H. Hubert)}

\hspace{2mm}

\cvitem{2019/2020}{Advanced Tax Theory (Master, in English. TA of Pr.F. Moizeau); Monetary Economics (Bachelor, in English. TA of Pr. T. Razafindrabe); Macroeconomics (Bachelor, in English. TA of Pr.M.H. Hubert)} 

%----------------------------------------------------------------------------------------
%	Other activities
%----------------------------------------------------------------------------------------

\section{Other activities}

Co-organizer of the GATE-LAB seminars; Co-organizer of the Project Doc Seminar; Representative of Ph.D students at the Doctoral School (EDGE) and the CREM research center; Treasury accountant for the Ph.D association PROJECT.

\

\textbf{Refereeing}: Annals of Regional Science, Social Choice and Welfare


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{}{English (Fluent), French (Fluent), Italian (Mothertongue), German (Work in progress)}{}

%----------------------------------------------------------------------------------------
%	Awards and scholarships
%----------------------------------------------------------------------------------------

\section{Scholarships}


\cvitem{2021}{Scholarship for visiting semester abroad financed by \textit{Région Bretagne} (2400 €)}
\cvitem{2020}{CREM funding (4000 €) \& POPSU funding (3000 €)  for online experiment }
\cvitem{2018-2021}{French Ph.D Scholarship}
\cvitem{2017-2018}{Double degree program Scholarship (5000 €)}

%----------------------------------------------------------------------------------------
%	PROGRAMMING
%----------------------------------------------------------------------------------------

\section{Computer Skills}

\cvitem{}{R (data-cleaning and data-analysis), STATA (mainly data-analysis), Python (simulations, web-scrapping), LimeSurvey (online surveys)} 

%----------------------------------------------------------------------------------------

\end{document}